{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-09-18 documents/application.tex
Assay still didn't work! Darnit!
Drum shaker thing
Soliton 1

Applying microwave power to the body is already used extensively in diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect). While the majority of diathermy systems use much lower frequencies for deeper heating penetration, several papers have explored the 10 GHz band.

@@

$$S = \frac{|E|^2}{Z_0}$$

@@

@@

>>>>

Applying microwave power to the body is already used extensively in diathermy (the internal heating of tissue for therapeutic effect) and hyperthermy (the overheating or cauterization of tissue for destructive effect). While the majority of diathermy systems use much lower frequencies for deeper heating penetration, several papers have explored the 10 GHz band. Superficial vs deep-tissue hyperthermia.

@@

@@

While such waveguide applicators provide excellent efficiency, at these frequency ranges the area of high field is quite tightly concentrated and may not be

@@

It is difficult to intuit how 40,000 watts can possibly be safe. It's useful to note, however, that the total energy dissipated in each pulse is . An oft-cited figure for the energy in a whisper is 10 mJ[wolframalpha]; and, while no clinical data are available, whispering into someone's chest is rarely considered calamitous.

Thermoacoustic effects should also be considered.

### 2020-09-18 documents/safety.tex
Soliton 1

>>>>

One could subsist on non-thermal effects literature alone. There is drama, mystery, intrigue, paragraphs of sardonic ire; ad-hominem analogies; effects spanning 10 orders of magnitude in strength and scale; where the tiniest of atomic murmurs sparks.

The picture is certainly much more complicated than "non-ionizing cannot have effects".
